---
title: "Lab 2"
author: "Ryan Morgan"
date: "February 2, 2017"
output: pdf_document
---

```{r}
movies <- read.csv(file=".//data//movies.csv")

head(movies)

library(tidyverse)

```

The structure of the data is 10,327 rows and 12 columns. The 12 variables are:

Date: Year-month-day
Rank
Rank.Last.Week
Days
Movie
Distributor
Gross
Change
Total.Gross
Release
Theaters
Per.Theater

#What were the most successful movies over the past two years? Make sure to define how you measure success. What can you say about movies that only came out recently?




We can find the maximum total gross for each movie, then find the movies with the highest total gross.

```{r}
movies %>% group_by(Movie) %>% summarise(MaxTotalGross = max(Total.Gross)) %>% arrange(desc(MaxTotalGross)) %>% head(20)
                                                  ```



Instead of looking at maximums, we can also look at averages. We can look at what the average gross was for each movie.

```{r}
movies %>% group_by(Movie) %>% summarise(MeanGross = mean(Gross)) %>% arrange(desc(MeanGross)) %>% head(20)
```

Average Rank:

```{r}
movies %>% group_by(Movie) %>% summarise(MeanRank = mean(Rank)) %>% arrange(MeanRank) %>% head(20)
```

Weeks at Number 1:

```{r}
movies %>% group_by(Movie) %>% summarise(WeeksAtOne = sum(Rank==1)) %>% arrange(desc(WeeksAtOne)) %>% head(20)
```
Weeks in Top 5:
```{r}
movies %>% group_by(Movie) %>% summarise(WeeksAtOne = sum(Rank<6)) %>% arrange(desc(WeeksAtOne)) %>% head(20)
```

Weeks in Top 10:
```{r}
movies %>% group_by(Movie) %>% summarise(WeeksAtOne = sum(Rank<11)) %>% arrange(desc(WeeksAtOne)) %>% head(20)
```

###### AMY WILL MAKE A TABLE to summarize these measures of success.


#How long, on average, are movies in theaters? Also look at the median time. Try to figure out what contributes to the big difference.


Mean Days in Box Office:
```{r}
movies %>% group_by(Movie) %>% summarise(DaysInBoxOffice = max(Days)) %>% summarise(MeanBORun = mean(DaysInBoxOffice))
```
Median Days in Box Office:
```{r}
movies %>% group_by(Movie) %>% summarise(DaysInBoxOffice = max(Days)) %>% summarise(MedianBORun = median(DaysInBoxOffice))
```
To try and see what might be contributing to such a large difference in mean and median, we can look at a distribution of the days in the box office. 

```{r}
daysinBO <- movies %>% group_by(Movie) %>% summarise(DaysInBoxOffice = max(Days))

daysinBO %>%ggplot(aes(DaysInBoxOffice)) + geom_histogram()
```
Well then. There appears to be a huge outlier on the high end. We can look at what movies have had the longest run in the box office. 

```{r}
daysinBO %>% arrange(desc(DaysInBoxOffice)) %>% head(20)

```
Apparently there are some movies that have been in theaters for more than 20,000 days. The 20th longest running film in the data set is "Time Changer," which has run for 4,945 days. This is more than 13 years. That would explain why the mean is so much larger than the median. 

It appears that movies that run this long are abnormal. We can try and find a cut-off point where we can look at a more reasonable distribution.


Looking at our original histogram, it looks like most of the data is clustered around somewhere less than 1000

```{r}
daysinBO %>%ggplot(aes(DaysInBoxOffice)) + geom_histogram()+xlim(c(0,1000))

```
After zooming in, we still have a very skewed distribution. We can continue to zoom in and the distribution will still be skewed.
```{r}
daysinBO %>%ggplot(aes(DaysInBoxOffice)) + geom_histogram()+xlim(c(0,300))
```
So the reason the mean is so much larger than the median is the distribuiton is very skewed to the right. The outliers pull the mean up to an extrememly high value, while the median is relatively unaffected by the outliers. 

#What is the standard trajectory of a movie's total gross? Draw a plot and label some of the trajectories. 



```{r}
length(unique(movieGross$Movie))

movieGross <- movies %>% select(Movie,Date,Gross)

movieGross %>% ggplot(aes(x=Date, y=Gross, group=Movie)) + geom_line()

```
